---
title: "day5-session1"
format: 
  html: 
    code-fold: true 
    code-summary: "Show me the code!" # simplify the code looks, but it is sensitive in space. 
editor: visual
execute: 
 echo: true # whether code shows up
 warning: false # cleaner version of not showing worning message
---

```{r}
library(tidyverse) 
```

## Explore starwars dataset

-   Look at the first 6 lines of starwars

    ```{r}
    head(starwars)
    ```

-   find the dimensions of starwars

    ```{r}
    dim(starwars)
    ```

-   Make a histogram of character heights

    ```{r}
    ggplot(data = starwars, aes(x=height)) + 
      geom_histogram()
    ```

-   Make a scatterplot of height v. weight

```{r}
ggplot(data = starwars, aes(x=height, y=mass, color = sex)) + 
  geom_jitter() +
  labs(x = "height (cm)", y= "mass (kg)", title = "height v. weight")
```

## Calculate summary statistics 

use mean() function to find means.

use sd() function to find standard deviations.

```{r}
mean_height <- mean(starwars$height, na.rm = TRUE)
mean_height
sd_height <- sd(starwars$height, na.rm = TRUE)
sd_height
class(sd_height)
# na.rm = FALSE: not to remove NA value / TRUE: remove NA value
```

# In-line reporting using code outputs

The mean height of star wars characters is `r mean_height`cm with a standard deviation of `r sd_height` cm.

